Cluster Difference Imaging Photometric Survey. IV. TOI 1937Ab. Youngest Hot Jupiter, or Just Tidally Spun Up?

### 2021-02-24 planet_paper/ms.tex
planet paper: sketch some intro

Lorem ipsum.

>>>>

Processes that have been suggested to produce hot Jupiters occur on
timescales ranging from megayears to gigayears (CITE, CITE, CITE).
One way to distinguish between these processes is therefore to find
young ($\lesssim$100\,Myr) hot Jupiters.  However the search for
sub-100\,Myr hot Jupiters has yielded remarkably few, if any, secure
detections.

Transits have provided a pile of tantalizing candidates.  HIP\,67522b,
with an age, orbital period, and size of XX\,Myr, X.X\,days, and
TOOSMALL\,$R_\oplus$ respectively, comes close
\citep{rizzuto_tess_2020}.  Its
size however is smaller than expected for a Jovian-mass object given
its age, by a factor of $\approx1.5\times$ (CITE Burrows, Fortney,
Thorngren models, CITE Owen 2020 entropy).  A mass measurement is
therefore needed to resolve its status as either a hot Jupiter, or an
inflated Neptunian world.  No other planet comes as close to fitting
the bill.  V1298 Tau b, part of a unique system with at least four
transiting planets, has the correct size and age. However its orbital
period (XX\,days) is too long to be a hot Jupiter (CITE David 2019,
2020).  The dips in PTFO 8-8695, long-interpreted as a candidate hot
Jupiter, are chromatic and show a changing orbital phase.  This is
inconsistent with a planetary interpretation (van Eyken 2012, Yu+15,
Onitsuka+17, Tanimoto+20, Bouma+20).

Reports of very young hot Jupiters have come from the radial velocity
(RV) technique, but these reports are difficult to verify.  TW Hya
(age=X\,Myr), for instance, showed a radial velocity semi-amplitude of
$\approx$200\,m\,s$^{-1}$ with a period of 3.6\,days, as measured in
optical spectra \citep{setiawan_young_2008} (CITE age reference).
Even though \citet{setiawan_young_2008} observed no significant
correlation between activity indicators and the RV signal, subsequent
infrared velocities measured by \citet{huelamo_tw_2008} showed small
variations $\lesssim 35\,$m\,s$^{-1}$.  \citet{huelamo_tw_2008}
ultimately concluded that activity-induced variations were the source
of the optical signal.  More recently, very young hot Jupiters have
been reported around CI Tau, V830 Tau, and TAP 26
\citep{johns-krull_CI_Tau_candidate_2016,donati_hot_2016,donati_hot_2017,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
The planetary nature of at least two of these signals (CI Tau and V830
Tau) has been debated \citep{donati_magnetic_2020,damasso_gaps_2020}.
More generally, the Bayesian model comparison problem of ``stellar
activity alone'' versus ``stellar activity plus planet'' has been
shown to require significant amounts of both data and statistical
machinery \citep[{\it
e.g.},][]{barragan_radial_2019,klein_simulated_2020} To date, none of
the reported young hot Jupiter detections have performed this style of
analysis.  Such an analysis, or else the acquisition of multi-color
radial velocities, seems like a requirement given the challenges of
detecting small signals in the presence of significant stellar
variability.

So where does that leave the search for young hot Jupiters?
A quick query to the NASA Exoplanet Archive yields the current state
of the search.
(FIGURE: Rp vs Age, and Mp\,sini vs Age).
